Introducing statistics with \\texttt{intRo}

### 2014-12-11 student-paper-competition-2014/paper.Rmd
New powerpoint file and image updates

\begin{figure*}[ht!]
\centering
\includegraphics[width=\linewidth]{images/ui_annotate.png}
\caption{The five elements that comprise the \texttt{intRo} application: 1) top navigation, 2) side navigation, 3) options panel, 4) results panel, and 5) code panel.}
\label{fig:ui}
\end{figure*}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=\linewidth]{images/app_creation_modules.png}
\caption{This figure depicts how the \texttt{server.R} and \texttt{ui.R} files are populated using the modular structure within \texttt{intRo}.}
\label{fig:app_creation_modules}
\end{figure*}

@@

## Generates the UI tabs
mylist <- list()
old_heading <- ""
for (i in 1:nrow(module_info)) {
    if (module_info[i,1] != old_heading) {
        if (i != 1) mylist[[length(mylist) + 1]] <- "-----"
        mylist[[length(mylist) + 1]] <- as.character(module_info[i,1])
        old_heading <- module_info[i,1]
    }
    mylist[[length(mylist) + 1]] <- get(paste(module_info[i,2], "ui", sep = "_"))
}

## Create the UI
shinyUI(
    navbarPage("intRo", id="top-nav",  theme = "bootstrap.min.css",
               tabPanel(title="", icon=icon("home"),
                        fluidRow(
                            do.call(navlistPanel, c(list(id = "side-nav", widths = c(2, 10)), mylist))
                        )
               ), ...
    ))
```
\normalsize

@@

\begin{table}[ht!]
\centering
\begin{tabular}{|c|c|c|}
\hline
Plot Type&X Variable Type Allowed&Y Variable Type Allowed\\
\hline
Histogram&Numeric&N/A\\
Normal Quantile Plot&Numeric&N/A\\
Scatterplot&Numeric&Numeric\\
Line Chart&Numeric&Numeric\\
Boxplot&Categorical&Numeric\\
Bar Chart&Categorical&Numeric\\
Pareto Chart&Categorical&Numeric\\
Mosaic Plot&Categorical&Categorical\\
\hline
\end{tabular}
\label{tab:plottypes}
\caption{The plot and variable types allowed in \texttt{intRo}'s graphical module. For example, when the selected plottype is histogram, the interface displays only a single variable selection box (x), and the variables selectable in this box are only numeric. If a boxplot is selected, the x variable must be categorical and the y variable must be numeric, and the list of choices updates automatically to reflect this.}
\end{table}
Part two of this text discusses probability and sampling distributions, which is outside the current realm of \texttt{intRo}, but part three focuses on inferential statistics. The inferential statistics include confidence intervals, hypothesis testing, and comparing two variables, all supported natively in \texttt{intRo}. Finally, part four of the text discusses the association between variables, including regression, functions that \texttt{intRo} performs with ease. Some of the more advanced topics of this section are currently unsupported by \texttt{intRo}, including multiple regression and nonparametric statistics.

>>>>

\begin{figure*}[ht!]
\centering
\includegraphics[width=\linewidth]{images/ui_annotate.pdf}
\caption{The five elements that comprise the \texttt{intRo} application: 1) top navigation, 2) side navigation, 3) options panel, 4) results panel, and 5) code panel.}
\label{fig:ui}
\end{figure*}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[width=\linewidth]{images/app_creation_modules.pdf}
\caption{This figure depicts how the \texttt{server.R} and \texttt{ui.R} files are populated using the modular structure within \texttt{intRo}.}
\label{fig:app_creation_modules}
\end{figure*}

@@

## mylist is a list containing the different ui module code
## Create the UI
shinyUI(
    navbarPage("intRo", id="top-nav",  theme = "bootstrap.min.css",
               tabPanel(title="", icon=icon("home"),
                        fluidRow(
                            do.call(navlistPanel, c(list(id = "side-nav", widths = c(2, 10)), mylist))
                        )
               ), ...
    ))
```
\normalsize

@@

\begin{table*}[ht!]
\centering
\begin{tabular}{|c|c|c|}
\hline
Plot Type&X Variable Type Allowed&Y Variable Type Allowed\\
\hline
Histogram&Numeric&N/A\\
Normal Quantile Plot&Numeric&N/A\\
Scatterplot&Numeric&Numeric\\
Line Chart&Numeric&Numeric\\
Boxplot&Categorical&Numeric\\
Bar Chart&Categorical&Numeric\\
Pareto Chart&Categorical&Numeric\\
Mosaic Plot&Categorical&Categorical\\
\hline
\end{tabular}
\label{tab:plottypes}
\caption{The plot and variable types allowed in \texttt{intRo}'s graphical module. For example, when the selected plottype is histogram, the interface displays only a single variable selection box (x), and the variables selectable in this box are only numeric. If a boxplot is selected, the x variable must be categorical and the y variable must be numeric, and the list of choices updates automatically to reflect this.}
\end{table*}
Part two of this text discusses probability and sampling distributions, which is outside the current realm of \texttt{intRo}, but part three focuses on inferential statistics. The inferential statistics include confidence intervals, hypothesis testing, and comparing two variables, all supported natively in \texttt{intRo}. Finally, part four of the text discusses the association between variables, including regression, functions that \texttt{intRo} performs with ease. Some of the more advanced topics of this section are currently unsupported by \texttt{intRo}, including multiple regression and nonparametric statistics.
